---
title: "k-NN regression"
subtitle: "Introduction to statistical Learning"
author: "Pedro Delicado and Alex Sánchez"
output:
  html_document:
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE, eval=FALSE, warning =FALSE, message=FALSE)
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)
```

# Introduction

The $k$ nearest-neighbor estimator of 
$m(t)=E(Y|X=t)$ is defined as
$$
\hat{m}(t) = \frac{1}{k} \sum_{i\in N_k(t)} y_i,
$$
where $N_k(t)$ is the neighborhood of $t$ defined by the $k$ closest points $x_i$ in the training sample.

## Data for prediction

The Boston housing data, included in the `MASS` package, contains information on housing in the Boston suburbs area.

```{r, echo=TRUE, eval=TRUE}
library(MASS)
# help(Boston)
data(Boston)
```

## Main predicion goal

Our goal is to predict the housing mean value, stored in the `mdev` variable, using as predictor variable the percentage of population with lower socio-economic status. `lstat`.

## Data description

We start by plotting the values to show the relation among them.

```{r, echo=TRUE, eval=TRUE, fig.asp=1, fig.width=4, fig.align='center'}
x <- Boston$lstat
y <- Boston$medv
plot(x,y, xlab="x: lstat", ylab="y: medv")
```

We migt consider fitting a polynomial curve but we start with KNN

# Building a model with KNN

We write a function for computing the $k$-nn estimator of $m(t)$ for a given value of $t_j\in \{t_1,\ldots,t_J\}$.

```{r}
knn_regr<- function(x, y, t=NULL, k=3, dist.method = "euclidean"){
	nx <- length(y)
	if (is.null(t)){ 
		t<- as.matrix(x) 
	} else {
		t<-as.matrix(t)
	}
	nt <- dim(t)[1]
	Dtx <- as.matrix( dist(rbind(t,as.matrix(x)),
	method = dist.method) )
	Dtx <- Dtx[1:nt,nt+(1:nx)]
	mt <- numeric(nt)
	for (j in 1:nt){
		d_t_x <- Dtx[j,]
		d_t_x_k <- sort(d_t_x,partial=k)[k]
		N_t_k <- unname( which(d_t_x <= d_t_x_k) )
		mt[j]=mean(y[N_t_k])
	}
	return(mt)
}	
```

Now this function is used to build a knn regression model.

Define $t$ as a sequence from 1 to 40 `t <- 1:40`.

```{r}
t <- 1:40
```

Estimate $m($`t[j]`$)$ for $j=1,\ldots,40$ using $k=50$.

```{r}
k <- 50
mt <- knn_regr(x, y, t=t, k=k, dist.method = "euclidean")
```

Plot `y` against `x`. Then represent the estimated regression function.

```{r}
plot(x,y,col=8, xlab="x: lstat", ylab="y: medv")
lines(t,mt,col=2,lwd=4)
title(main=paste0("k-nn with k=",k))
```

## Tuning the model 

Repeat the same process using different values of $k$. 

```{r}
k_values <- c(100, 50, 15, 5)

for (k in k_values) {
    mt <- knn_regr(x, y, t=t, k=k, dist.method = "euclidean")
    
    plot(x, y, col=8, xlab="x: lstat", ylab="y: medv", 
         main=paste0("k-NN con k=", k))
    lines(t, mt, col=2, lwd=4)
}

```

# Model performance

A simple, though not good, idea is to compute the resubstitution (or training) error associated with each model.

When evaluating the performance of a statistical learning model, it is important to distinguish between **training error** (also called **resubstitution error**) and **test error**. In this document, we explain why training error can be misleading and how to properly assess model performance.

## What is Training Error?

Training error is calculated by evaluating the model's predictions on the same dataset that was used to fit the model. Mathematically, it is computed as:

$$
\text{Training Error} = \frac{1}{n} \sum_{i=1}^{n} (y_i - \hat{m}(x_i))^2
$$

where:
- \( y_i \) are the observed values,
- \( \hat{m}(x_i) \) are the predicted values from the model,
- \( n \) is the total number of observations.


### Why is Training Error Misleading?

Since the model is evaluated on the same data it was trained on, the training error is **overly optimistic** and does not provide a reliable measure of how well the model generalizes to new data. This issue is particularly problematic when dealing with flexible models such as **k-nearest neighbors (k-NN)**.

### Example: k-NN and Overfitting

In k-NN regression, the choice of \( k \) significantly affects the training error:
- When \( k \) is **very small**, the model closely follows the training data, leading to **low training error but high test error (overfitting)**.
- When \( k \) is **too large**, the model smooths out the predictions too much, leading to **higher training and test error (underfitting)**.


```{r}
k_values <- c(200, 100, 50, 15, 5, 3)

errors <- data.frame(k = integer(), RMSE = numeric())


for (k in k_values) {
    mt <- knn_regr(x, y, t=t, k=k, dist.method = "euclidean")
    

    RMSE <- sqrt(mean((y - mt)^2))  
    
    errors <- rbind(errors, data.frame(k = k, RMSE = RMSE))
    
    plot(x, y, col=8, xlab="x: lstat", ylab="y: medv", 
         main=paste0("k-NN con k=", k, " (RMSE: ", round(RMSE, 2), ")"))
    lines(t, mt, col=2, lwd=4)
}

print(errors)

```


## A Better Approach: Using Test Error

To properly evaluate model performance, we must estimate the **test error**, which is computed on a separate dataset that was **not used for training**. This can be done by:
1. **Splitting the data** into a **training set** and a **test set**.
2. **Training the model** on the training set.
3. **Evaluating the model** on the test set and computing the test error:

$$
\text{Test Error} = \frac{1}{m} \sum_{j=1}^{m} (y_j^{\text{test}} - \hat{m}(x_j^{\text{test}}))^2
$$

where:
- \( y_j^{\text{test}} \) are the actual test values,
- \( \hat{m}(x_j^{\text{test}}) \) are the model's predictions on the test set,
- \( m \) is the number of test observations.


Using training error alone can give a **false sense of accuracy**. Instead, we should always assess model performance on unseen data (test set) to ensure that our model generalizes well. In the next section, we will implement k-NN regression with a **train-test split** to correctly measure prediction error.

### An (improved) example

```{r}
k_values <- c(200, 100, 50, 15, 5, 3)

errors <- data.frame(k = integer(), Training_RMSE = numeric(), Test_RMSE = numeric())

set.seed(123)
n <- length(y)
train_index <- sample(1:n, size = floor(0.8 * n), replace = FALSE)

x_train <- x[train_index]
y_train <- y[train_index]

x_test <- x[-train_index]
y_test <- y[-train_index]


for (k in k_values) {
    mt_train <- knn_regr(x_train, y_train, t=x_train, k=k, dist.method = "euclidean")
    
    mt_test <- knn_regr(x_train, y_train, t=x_test, k=k, dist.method = "euclidean")
    
    RMSE_train <- sqrt(mean((y_train - mt_train)^2))  
    RMSE_test <- sqrt(mean((y_test - mt_test)^2))  
    
    errors <- rbind(errors, data.frame(k = k, Training_RMSE = RMSE_train, Test_RMSE = RMSE_test))
    
    plot(x_train, y_train, col=8, xlab="x: lstat", ylab="y: medv", 
         main=paste0("k-NN con k=", k, " (Train RMSE: ", round(RMSE_train, 2), 
                      ", Test RMSE: ", round(RMSE_test, 2), ")"))
    
    t_seq <- seq(min(x), max(x), length.out=100)
    mt_seq <- knn_regr(x_train, y_train, t=t_seq, k=k, dist.method = "euclidean")
    lines(t_seq, mt_seq, col=2, lwd=4)
}

print(errors)

```


# Step-by-step Explanation of the knn_regr Function

The function `knn_regr` implements **k-nearest neighbors (k-NN) regression**. This method estimates the conditional expectation \( E(Y | X = t) \) by averaging the values of the \( k \) closest neighbors of \( t \) in the training data. Below, we explain each step of the function in detail.


This function provides a simple implementation of k-NN regression by computing distances, identifying the nearest neighbors, and averaging their response values. 

## Function Code

```{r}
knn_regr <- function(x, y, t=NULL, k=3, dist.method = "euclidean") {
    nx <- length(y)  # Number of observations in the training data
    
    # If t is not provided, use x as the set of query points
    if (is.null(t)) { 
        t <- as.matrix(x) 
    } else {
        t <- as.matrix(t)
    }
    
    nt <- dim(t)[1]  # Number of query points
    
    # Compute the distance matrix between each t[j] and all x[i]
    Dtx <- as.matrix(dist(rbind(t, as.matrix(x)), method = dist.method))
    
    # Extract only the distances between test points and training points
    Dtx <- Dtx[1:nt, nt+(1:nx)]
    
    mt <- numeric(nt)  # Initialize the vector of predictions
    
    # Compute the k-NN estimate for each query point t[j]
    for (j in 1:nt) {
        d_t_x <- Dtx[j,]  # Distances from t[j] to all training points
        d_t_x_k <- sort(d_t_x, partial=k)[k]  # Distance to the k-th nearest neighbor
        N_t_k <- unname(which(d_t_x <= d_t_x_k))  # Indices of the k nearest neighbors
        
        mt[j] <- mean(y[N_t_k])  # Compute the mean response of k nearest neighbors
    }
    
    return(mt)  # Return the vector of estimated values
}
```

## Step-by-Step Explanation

### 1. Function Inputs

The function takes the following inputs:
- `x`: The vector of predictor values (training data).
- `y`: The corresponding response values.
- `t`: A vector of test points where we want to estimate \( E(Y | X = t) \). If `t` is not provided, it defaults to `x` (in-sample estimation).
- `k`: The number of nearest neighbors to consider.
- `dist.method`: The method used to compute distances (default: Euclidean).

### 2. Checking the Input `t`

If `t` is `NULL`, the function assigns `x` to `t`, meaning that predictions will be computed for the training points.

```{r eval=FALSE}
if (is.null(t)){ 
    t <- as.matrix(x) 
} else {
    t <- as.matrix(t)
}
```

### 3. Compute the Distance Matrix

The function calculates pairwise distances between every point in `t` and every point in `x` using the `dist` function.

```{r eval=FALSE}
dist.method <- "euclidean"
Dtx <- as.matrix(dist(rbind(t, as.matrix(x)), method = dist.method))
```

After computing the distance matrix, we extract only the distances between test points and training points:

```{r eval=FALSE}
Dtx <- Dtx[1:nt, nt+(1:nx)]
```

### 4. Find the k Nearest Neighbors

For each test point \( t[j] \):
- Extract the distances to all training points.
- Identify the **k-th smallest** distance.
- Select the indices of the **k closest** training points.

```{r eval=FALSE}
d_t_x <- Dtx[j,]  # Distances from t[j] to all training points
d_t_x_k <- sort(d_t_x, partial=k)[k]  # Distance to the k-th nearest neighbor
N_t_k <- unname(which(d_t_x <= d_t_x_k))  # Indices of the k nearest neighbors
```

### 5. Compute the k-NN Estimate

Once the nearest neighbors are identified, their corresponding `y` values are averaged to compute the estimate:

```{r eval=FALSE}
mt[j] <- mean(y[N_t_k])  # Compute the mean response of k nearest neighbors
```

### 6. Return the Estimated Values

Finally, the function returns the vector `mt` containing the estimated values for all test points.

```{r eval=FALSE}
return(mt)
```



