---
title: "Simulating a mixture of normals"
subtitle: "Introduction to statistical Learning"
author: "Pedro Delicado"
output:
  html_document:
---

> Reproducing the exemple in Section 2.3.3 of  
> "The Elements of Statistical Learning" 
> (Hastie, Tinshirani and Friedman, 2009)

First we generated 10 means $m_k$ from a bivariate Gaussian distribution $N((1, 0)^T , {\bf I})$ and labeled this class `BLUE` (0). Similarly, 10 more were drawn from $N((0, 1)^T , {\bf I})$ and labeled class `ORANGE` (1). 

```{r,fig.asp=1}
set.seed(321)
classes <- c(rep('BLUE',10), rep('ORANGE',10))
cte <- c(rep(1,10), rep(0,20), rep(1,10))
mk <- matrix(rnorm(20*2) + cte,
             ncol=2, byrow = FALSE) 
plot(mk[,1],mk[,2],col=classes,pch=19, asp=1)
```

Then for each class we generated 100 observations as follows: for each observation, we picked an $m_k$ at random with probability $1/10$, 
and then generated a $N(m_k, {\bf I}/5)$, thus leading to a mixture of Gaussian clusters
for each class. 

```{r,fig.asp=1}
N <- 100
smpl.B <- sample(1:10, size=N, replace=TRUE)
smpl.O <- 10 + sample(1:10, size=N, replace=TRUE)
xy <- matrix(rnorm(2*N*2)/sqrt(5), ncol=2) + 
  mk[c(smpl.B,smpl.O),]
class.xy <- c(rep('BLUE',N), rep('ORANGE',N))
plot(xy[,1],xy[,2], col=class.xy,asp=1)
points(mk[,1],mk[,2],col=classes,pch=19)
```

```{r}
df.xy <- data.frame(x=xy[,1],y=xy[,2],class=class.xy)
if (!file.exists("2clas2dim.csv")) 
  write.table(df.xy,file="2clas2dim.csv",dec=".",sep=";", row.names = FALSE)
```
