---
title: "Decision Trees Lab 1"
authors:
- Adapted by EVL, FRC and ASP
date: "`r Sys.Date()`"
format:
    html: 
      toc: true
      toc-depth: 3
      code-fold: show
      fig-width: 8
      fig-height: 6
    pdf: default
knit:
  quarto:
    chunk_options:
      echo: true
      cache: false
      prompt: false
      tidy: true
      comment: NA
      message: false
      warning: false
    knit_options:
      width: 75
reference-location: margin
execute:
    echo: true
    message: false
    warning: false
bibliography: "../StatisticalLearning.bib"
editor_options: 
  chunk_output_type: console
---

```{r packages, include=FALSE}
# If the package is not installed then it will be installed
if(!require("tree")) install.packages("tree")
if(!require("ISLR2")) install.packages("ISLR2")
if(!require("rsample")) install.packages("rsample")
if(!require("rpart.plot")) install.packages("rpart.plot")
if(!require("skimr")) install.packages("skimr")
if(!require("kableExtra")) install.packages("kableExtra")
```

# Classification Trees: Predicting car sales

## Introduction

This example has been adapted from the book "Introduction to Statistical Learning with R", [lab 8.3](https://hastie.su.domains/ISLR2/Labs/Rmarkdown_Notebooks/Ch8-baggboost-lab.Rmd). 

The authors have decided to use the R `tree` package, which is not the most powerful R package for trees, but offers a good compromise between power and flexibility.

The lab relies on the `Carseats` dataset, a simulated dataset, that is included with the book's package,  containing several variables about sales of child car seats at different stores.

```{r}
require(ISLR2)
data("Carseats")
# help("Carseats")
```

A data frame with 400 observations on the following 11 variables.

- `Sales`: Unit sales (in thousands) at each location
- `CompPrice`: Price charged by competitor at each location
- `Income`: Community income level (in thousands of dollars)
- `Advertising`: Local advertising budget for company at each location (in thousands of dollars)
- `Population`: Population size in region (in thousands)
- `Price`: Price company charges for car seats at each site
- `ShelveLoc`: A factor with levels Bad, Good and Medium indicating the quality of the shelving location for the car seats at each site
- `Age`: Average age of the local population
- `Education`: Education level at each location
- `Urban`: A factor with levels No and Yes to indicate whether the store is in an urban or rural location
- `US`: A factor with levels No and Yes to indicate whether the store is in the US or not

The first part of the lab will aim at predicting the variable `sales`. 

In order to apply classification trees first, we start by categorizing the `sales`variable. *This is not usually seen as a good strategy, so take it only for didactical purpose*.


## Data description

We use a generic name for the dataset, in order to facilitate code reuse.

```{r assignments}
myDescription <- "The data are a simulated data set containing sales of child car seats at different stores [@james2013introduction]"
mydataset <- Carseats
```

```{r, dataDescription}
n <- nrow(mydataset)
p <- ncol(mydataset)
```

There are ```r n``` rows and  ```r p``` columns.

The variable `Sales` is categorized  creating a new variable, `High`, which takes on a value of `Yes` if the `Sales` variable exceeds 8, and a value of `No` otherwise.

```{r}
# as.factor() changes the type of variable to factor
mydataset$High=as.factor(ifelse(mydataset$Sales<=8,"No","Yes"))
```

The number of observations for each class is:

```{r}
kable(table(mydataset$High), caption= "Number of observations for each class", col.names = c('High','Freq'))
```

The aim is of this study is to predict the categorical values of sales (`High`) using all variables but `Sales`.

It is a classification problem and we will build a *classification tree model*.

### Data summarization

This is a short data set summary

```{r}
summary(mydataset)
```

An improved description:

```{r}
skimr::skim(mydataset)
```

## Preprocess

It is very common that the data need to be preprocessed before training the model*

In this case, there seem to be no missing values, no outliers and most variables are decently symmetrical, so no cleaning or preprocessing are required.

## Train/Test partition of data

In order to properly evaluate the performance of a model, we must estimate the error rather than simply computing the training error.

With thhis aim in mind we proceed as follows: 

1.  split the observations into a training set and a test set,
2.  build the model using the training set, and
3.  evaluate its performance on the test data.

```{r, dataPartition}
set.seed(2)
pt <- 1/2
train <- sample(1:nrow(mydataset),pt*nrow(mydataset))
mydataset.test <- mydataset[-train,]
High.test <-  mydataset[-train,"High"]
```

The train and tets set have `r length(train)` `r nrow(mydataset) - length(train)` observations respectively.

In train data, the number of observations for each class is:

```{r showPartition}
kableExtra::kable(table(mydataset[train,"High"]), caption= "Train data: number of observations for each class", col.names = c('High','Freq'))
```

## Train model

We now use the `tree()` function to fit a classification tree in order to predict `High` using all variables but `Sales` using only de train set.

```{r modelTreeTrain}
library(tree)
tree.mydataset=tree(High~.-Sales, mydataset,
                    subset=train, 
                    split="deviance")
```

<!-- We might have also used `rpart` to build the tree -->

<!-- ```{r} -->
<!-- tree.mydataset2=rpart::rpart(High~.-Sales, mydataset, subset=train) -->
<!-- ``` -->

The `summary()` function lists the variables that are used as internal nodes in the tree, the number of terminal nodes, and the **training** error rate

```{r summarizeTreeTrain}
summary(tree.mydataset)
# summary(tree.mydataset2)
```

For classification trees the deviance of a tree (roughly equivalent to the concept of impurity) is defined  as the sum over all terminal leaves of:
$$
-2 \sum_m \sum_k n_{mk} log(\hat{p}_{mk}),
$$

where $n_{mk}$ is the number of observations in the `m`th terminal node that belong to the `k`th class. 

The *residual mean deviance* reported is simply the deviance divided by $n - |T_0|$ where $T_0$ is the number of terminal nodes.

## Plot the Tree

The next step is display the tree graphically. We use the `plot()` function to display the tree structure, and the `text()`function to display the node labels.

```{r plotTree1, fig.cap="Classification tree", fig.height=10, fig.width=12}
plot(tree.mydataset)
text(tree.mydataset,pretty=0, cex=0.6)
```


It is also possible to show a `R` print output corresponding to each branch of the tree.

```{r}
tree.mydataset
```

## Prediction

In order to properly evaluate the performance of a classification tree on these data, we must estimate the test error rather than simply computing the training error. 

We have split the observations into a training set and a test set, and the tree has been built using the training set.

After this, the tree performance  *is evaluated on the test data*. 
The `predict()` function can be used for this purpose.

```{r TreePerformance}
tree.pred=predict(tree.mydataset,mydataset.test,type="class")
res <- table(tree.pred,High.test)
res
accrcy <- sum(diag(res)/sum(res))
```

The accuracy is **`r accrcy`** or misclassification error rate is **`r 1-accrcy`**, which are respectively smaller and biiger than those computed from the tree built on the train data.

## Pruning the tree (Tunning model)

We know there is a chance that fitting the tree produces some overfitting so we can consider whether *pruning the tree* could lead to improved results.

The function `cv.tree()` performs cross-validation in order to determine the optimal level of tree complexity. 
- Cost complexity pruning is used in order to select a sequence of trees for consideration. 
- We use the argument `FUN = prune.misclass` in order to indicate that we want the *classification error rate* to guide the cross-validation and pruning process, rather than the default for the `cv.tree()` function, which is *deviance*. 

The `cv.tree()` function reports the number of terminal nodes of each tree considered (size) as well as the corresponding error rate and the value of the cost-complexity parameter used 

```{r prepareForPrunning}
set.seed(123987)
cv.mydataset=cv.tree(tree.mydataset,FUN=prune.misclass)
names(cv.mydataset)
cv.mydataset
```

Note that, despite the name, `dev` corresponds to the cross-validation error rate in this instance.

The output shows how, as the size of the tree increases, so does the deviance. 

This can be better visualized by plotting the error rate as a function of  `size`and `k`.

```{r errorRatePlot}
par(mfrow=c(1,2))
plot(cv.mydataset$size,cv.mydataset$dev,type="b")
plot(cv.mydataset$k,cv.mydataset$dev,type="b")
par(mfrow=c(1,1))
```

These plots can be used to suggest the best tree, but it can also be chosen automatically by taking the minimal value $k$ from the output of the `cv.tree` function.

```{r bestSize}
myBest <- cv.mydataset$size[which.min(cv.mydataset$dev)]
```

Now, the `prune.misclass()` function can be used to prune the tree and obtain a "best tree". If *we decide to call the best tree the one that has reached the smallest deviance* we can proceed as follows:

```{r pruneTheTree}
prune.mydataset=prune.misclass(tree.mydataset,best=myBest)
```


```{r plotPrunedTree, fig.cap="The best classification pruned tree", fig.height=10, fig.width=12}
plot(prune.mydataset)
text(prune.mydataset,pretty=0)
```

The tree is clearly smaller than the original one, but how well does this pruned tree perform on the test data set?

```{r testPrunedTree}
prunedTree.pred=predict(prune.mydataset,mydataset.test,type="class")
prunedRes <- table(prunedTree.pred,High.test)
prunedRes
prunedAccrcy <- sum(diag(prunedRes)/sum(prunedRes))
```

The accuracy is **`r prunedAccrcy`**.

If we increase the value of `best`, for example `r  cv.mydataset$size[1]` terminal nodes, we obtain a larger pruned tree with lower classification accuracy:

```{r prunedTree2, fig.cap="Other classification pruned tree", fig.height=10, fig.width=12}
prune.mydataset=prune.misclass(tree.mydataset, 
                               best = cv.mydataset$size[1])
plot(prune.mydataset)
text(prune.mydataset, pretty=0)
```

```{r predictPrunedTree2}
ptree.pred=predict(prune.mydataset, mydataset.test, type="class")
pres <- table(ptree.pred, High.test)
pres
paccrcy <- sum(diag(pres)/sum(pres))
```

The accuracy is **`r paccrcy`**.

**In conclusion** It can be seen that the difference in accuracy between the pruned tree and the original one is small. Indeed, changing the seed for splitting can lead to both smaller or bigger accuracy in the pruned tree than in the original one.

Obviously, the pruned tree is smaller so even if the original tree is slightly more accurate than the pruned one we might prefer the second one, because it is relying on less data to produce almost the same accuracy, whic is *something that most users usually prefer*.

## Predicting car sales with *regression* trees

A reasonable question is how would the accuracy of the trees be affected if, instead of categorizing sales we had used it "as.is", building a regression tree instead.

Although it may seem straightforward to answer this question by building a regression tree  using the approach described in next section, the fact is that it is no so immediate as it may seem.

The reason for this is that, if we wish to compare the perfomance of both approaches we need a common measure of accuracy. For regression trees the Mean Square Error is generally used, while accuracy or some other measures derived from the confusion matrix are common for classification trees. **Comparing those two measures, however, is not straightforward**. One may think of relying on some kind of information measure, that can be computed on both regresion and classification trees such as entropy or Kullback-Leiber divergence, but the problem then is how to derive such measure for both the classification and the regression trees.


# Regression Trees: Predicting numerical (response) variables

## The Car Sales problem (again)

Even if we do not aim at comparing regression and classification problems, the carseats problem proivides a good example on how to build and optimize a regression tree.

Remember our goal is to predict car sales from a simulated data set containing sales of child car seats at different stores [@james2013introduction]. In order to make sections reproducible, we reload the package and the data.

### Get the Data

```{r}
require(ISLR2)
data("Carseats")
mydataset <- Carseats
```

### Create tarin/test sets

We split original data into test and training sets.
Package `resample` allows to do a weighted splitting to enbsure that no class is underrepresented due to chance. If sample size is high this can usually be ignored.

```{r splitTestTrain}
# Split the data into training and test sets
set.seed(2)
pt <- 1/2
train <- sample(1:nrow(mydataset), pt * nrow(mydataset))
mydataset.test <- mydataset[-train,]
sales.test <- mydataset$Sales[-train]
```

### Build (and check) the model

```{r fitRegTree1}
# Fit the regression tree using the Sales variable

tree.mydataset <- tree(Sales ~ . , mydataset,
                       subset = train)

# Summary of the fitted regression tree
summary(tree.mydataset)
```


```{r plotRegTree1}
# Plot the regression tree
plot(tree.mydataset)
text(tree.mydataset, pretty = 0, cex = 0.6)
```

### Make prediction

```{r predictTree}
# Predict using the test data
tree.pred <- predict(tree.mydataset, mydataset.test)
```

### Estimate prediction error

A common measure of prediction error is the Mean Square Error.

Notice that it is computed from a direct substraction between the predicted sales and the original values in the test subset.

```{r checkRegTree}
mse1 <- mean((tree.pred - sales.test)^2)
mse1
```

The mean squared error obtained from the original tree is ```r mse1```.

### Optimize the tree

In order to optimize the trune we first compute the best cost-complexity parameter using cross-validation and then use it to prune the tree.

```{r costComplexityCompute}
# Prune the regression tree
set.seed(123987)
cv.mydataset <- cv.tree(tree.mydataset, FUN = prune.tree)
names(cv.mydataset)
cv.mydataset
```

Before selecting the best $\alpha$ value it may be useful to plot the MSE as a function of the tree size or of $\alpha$ itself. **Notice that $\alpha$ is named as "$k$" in the `tree` package.**

```{r costComplexityPlot}
# Plot the cross-validation error
par(mfrow = c(1, 2))
plot(cv.mydataset$size, cv.mydataset$dev, type = "b")
plot(cv.mydataset$k, cv.mydataset$dev, type = "b")
par(mfrow = c(1, 1))
```

It seems clear that, in this case, the smallest error is attained when the tree is not pruned (size=14), so the "best" value of $\alpha$ leads to not pruning the tree.


```{r costComplexityChoose}
# Choose the best tree size
myBest <- cv.mydataset$size[which.min(cv.mydataset$dev)]

# Prune the tree with the best size
prune.mydataset <- prune.tree(tree.mydataset, 
                              best = myBest)

# Plot the pruned regression tree
plot(prune.mydataset)
text(prune.mydataset, pretty = 0)

# Predict using the pruned tree
prunedTree.pred <- predict(prune.mydataset, mydataset.test)

# Calculate mean squared error for pruned tree
prunedMSE <- mean((prunedTree.pred - sales.test)^2)
prunedMSE
```

In this case, pruning does not improve the tree and the best tree is the one returned by the initial tun of the algorithm.

If however, we look for a compromise between the tree size and the deviance we can choose, based on the cv plots, a size of 6 or even 3:

```{r pruneto5}
# Prune the tree with the best size
pruneto5.mydataset <- prune.tree(tree.mydataset, 
                              best = 6)

# Plot the pruned regression tree
plot(pruneto5.mydataset)
text(pruneto5.mydataset, pretty = 0)

# Predict using the pruned tree
prunedTree5.pred <- predict(pruneto5.mydataset, mydataset.test)

# Calculate mean squared error for pruned tree
prunedMSE5 <- mean((prunedTree5.pred - sales.test)^2)
prunedMSE5
```


```{r pruneto3}
# Prune the tree with the best size
pruneto3.mydataset <- prune.tree(tree.mydataset, 
                              best = 3)

# Plot the pruned regression tree
plot(pruneto3.mydataset)
text(pruneto3.mydataset, pretty = 0)

# Predict using the pruned tree
prunedTree3.pred <- predict(pruneto3.mydataset, mydataset.test)

# Calculate mean squared error for pruned tree
prunedMSE3 <- mean((prunedTree3.pred - sales.test)^2)
prunedMSE3
```

Clearly, *the best compromise seems to prune with a size of 5, which hardly increases the MSE while providinga good simplification of the tree*


## Predicting Boston house prices

This example is borrowed from [@amat2017].

The `Boston` dataset available in the `MASS` package contains housing prices for the city of Boston, as well as socioeconomic information for the neighborhood in which they are located.

```{r loadBostonDat}
library(ISLR2)
data("Boston")
datos <- Boston
head(datos, 3)
```

Our goal is to fit a regression model that allows predicting the average price of a home (`medv`) based on the available variables.


A quick visualization of the available variables shows that, not only they are of mixed types, but also the relation between them is far from linear inmost if not all cases.

```{r, BostonPlotVars, fig.align='center'}
color <- adjustcolor("forestgreen", alpha.f = 0.5)
ps <- function(x, y, ...) {  # custom panel function
  panel.smooth(x, y, col = color, col.smooth = "black", 
               cex = 0.7, lwd = 2)
}
nc<- ncol(datos)
pairs(datos[,c(1:6,nc)], cex = 0.7, upper.panel = ps, col = color)
# pairs(datos[,c(7:14)], cex = 0.7, upper.panel = ps, col = color)

```

This is a good scenario to consider regression trees as a good option.

### Model fitting

Create a train and test sets

```{r BostonSplitTestTrain}
set.seed(123)
train <- sample(1:nrow(datos), size = nrow(datos)/2)
datos_train <- datos[train,]
datos_test  <- datos[-train,]
```

We use the `tree` function of the `tree` package to build the model. This function grows the tree until it meets a stop condition. By default, these conditions are:

- `mincut`: minimum number of observations that at least one of the child nodes must have for the division to occur.
- `minsize`: minimum number of observations a node must have in order for it to be split.

```{r BostonFitTree1}
set.seed(123)
regTree<- tree::tree(
                    formula = medv ~ .,
                    data    = datos_train,
                    split   = "deviance",
                    mincut  = 20,
                    minsize = 50
                  )
summary(regTree)
```

The `summary` shows that the trained tree has a total of 6 terminal nodes and that the variables `rm, lstat, dis` and `tax` have been used as predictors.

In the context of regression trees, the `Residual mean deviance` term is the residual sum of squares divided by (number of observations - number of terminal nodes). The smaller the deviance, the better the fit of the tree to the training observations.

The tree can be visualized:

```{r BostonPlotTree}
par(mar = c(1,1,1,1))
plot(x = regTree, type = "proportional")
text(x = regTree, splits = TRUE, pretty = 0, cex = 0.8, col = "firebrick")
```

### Prunning the tree

We use the `cv.tree` function that uses cross validation to identify the optimal penalty value. By default, this function relies on the *deviance* to guide the pruning process.

We **grow the tree again** with less restrictive parameters so we have a big tree to prune:

```{r BostonFitBigTree}
regTree2<- tree::tree(
                    formula = medv ~ .,
                    data    = datos_train,
                    split   = "deviance",
                    mincut  = 1,
                    minsize = 2,
                    mindev  = 0
                  )
```


```{r BostonComputeComplexity}

set.seed(123)
cv_regTree2 <- tree::cv.tree(regTree2, K = 5)
```

The function returns an object `cv_regTree2` containing:

- `size`: The size (number of terminal nodes) of each tree.
- `dev`: The cross-validation test error estimate for each tree size.
- `k`: The range of penalty values $\alpha$ evaluated.
- `method`: The criteria used to select the best tree.

These can be used to visualize and understand the optimization performed.

```{r BostonOptimalAlpha}
optSize <- rev(cv_regTree2$size)[which.min(rev(cv_regTree2$dev))]
paste("Optimal size obtained is:", optSize)
```

```{r BostonPlotAlphas}
library(ggplot2)
library(ggpubr)


resultados_cv <- data.frame(
                   n_nodes  = cv_regTree2$size,
                   deviance = cv_regTree2$dev,
                   alpha    = cv_regTree2$k
                 )

p1 <- ggplot(data = resultados_cv, aes(x = n_nodes, y = deviance)) +
      geom_line() + 
      geom_point() +
      geom_vline(xintercept = optSize, color = "red") +
      labs(title = "Error vs tree size") +
      theme_bw() 
  
p2 <- ggplot(data = resultados_cv, aes(x = alpha, y = deviance)) +
      geom_line() + 
      geom_point() +
      labs(title = "Error vs penalization (alpha)") +
      theme_bw() 

ggarrange(p1, p2)
```

Once the optimal value identified, the final pruning is applied with the `prune.tree` function. This function also accepts the optimal value of $\alpha$ instead of size.

```{r BostonPruneTree}
finalTree <- tree::prune.tree(
                  tree = regTree2,
                  best = optSize
               )

par(mar = c(1,1,1,1))
plot(x = finalTree, type = "proportional")
text(x = finalTree, splits = TRUE, pretty = 0, cex = 0.8, col = "firebrick")
```

### Predicting and checking model accuracy

We can use both, original and pruned trees to predict the data for the test set.

The quality of the prediction is based in the Root Mean Square.

For the original tree one has:

```{r BostonPredictAndCheck1}
predicciones <- predict(regTree, newdata = datos_test)
test_rmse    <- sqrt(mean((predicciones - datos_test$medv)^2))
paste("Error de test (rmse) del árbol inicial:", round(test_rmse,2))
```

And for the final tree:

```{r BostonPredictAndCheckFinal}
predicciones_finales <- predict(finalTree, newdata = datos_test)
test_rmse    <- sqrt(mean((predicciones_finales - datos_test$medv)^2))
paste("Error de test (rmse) del árbol final:", round(test_rmse,2))
```

That is *The error associated with the prediction has slightly decreased, while the tree is much simpler*. 

**That is what we ideal are aiming at!**

# Alternative packages for CART

## Comparison between `caret`, `rpart`, and `tree`

Two popular packages for working with decision trees are `rpart` and `tree`. Both offer functionalities for building and visualizing decision trees. The table below shows a comparison between the main functions of these packages, as well as `caret`, which is a generic framework for performing classification and prediction tasks, including trees.

### Table: Comparison of important functions for working with decision trees

| **Function / Package**              | **tree**                                        | **rpart**                                      | **caret**                               |
|-------------------------------------|-------------------------------------------------|------------------------------------------------|-----------------------------------------|
| **Building Decision Tree**          | **`tree()`**                                    | **`rpart()`**                                 | **`train()`** with method = "rpart"      |
| **Visualizing Decision Tree**       | -                                               | **`plot()`**                                  | **`plot()`** with type = "text"         |
| **Pruning Decision Tree**           | **`cv.tree()`**                                 | **`prune()`**                                 | **`train()`** with method = "rpart" and tuneLength > 1 |
| **Evaluating Model Performance**    | -                                               | **`predict()`**                               | **`train()`** with method = "rpart" and metric = "Accuracy" |
| **Handling Missing Values**         | **`na.action`**                                 | **`na.action`**                               | **`preProcess()`** with method = "medianImpute" |
| **Tuning Hyperparameters**          | -                                               | **`rpart.control()`**                         | **`train()`** with method = "rpart" and tuneGrid argument |
| **Visualizing Variable Importance** | -                                               | **`importance()`**                            | **`varImp()`**                         |

### Examples of usage:

| **Function / Package**              | **tree**                                        | **rpart**                                      | **caret**                               |
|-------------------------------------|-------------------------------------------------|------------------------------------------------|-----------------------------------------|
| **Building Decision Tree**          | **`tree(Species ~ ., data = iris)`**           | **`rpart(Species ~ ., data = iris)`**         | **`train(Species ~ ., method = "rpart", data = iris)`**      |
| **Visualizing Decision Tree**       | -                                               | **`plot(fit)`**                               | **`plot(fit, type = "text")`**         |
| **Pruning Decision Tree**           | **`cv.tree(Species ~ ., data = iris)`**        | **`prune(fit, cp = 0.02)`**                  | **`train(Species ~ ., method = "rpart", data = iris, tuneLength = 5)`** |
| **Evaluating Model Performance**    | -                                               | **`pred <- predict(fit, iris, type = "class")`** | **`train(Species ~ ., method = "rpart", data = iris, metric = "Accuracy")`** |
| **Handling Missing Values**         | **`tree(Species ~ ., data = na.omit(iris))`**  | **`rpart(Species ~ ., data = na.omit(iris), na.action = na.rpart)`** | **`preProcess(iris, method = "medianImpute")`** |
| **Tuning Hyperparameters**          | -                                               | **`rpart(Species ~ ., data = iris, control = rpart.control(cp = c(0.001, 0.01, 0.1)))`** | **`train(Species ~ ., method = "rpart", data = iris, tuneGrid = expand.grid(cp = c(0.001, 0.01, 0.1)))`** |
| **Visualizing Variable Importance** | -                                               | **`importance(fit)`**                         | **`varImp(fit)`**                      |

These examples illustrate how to perform various tasks related to decision trees using the `tree`, `rpart`, and `caret` packages. Each package has its own syntax and set of functions, so they can be used according to the user's needs and preferences.


# Exercises

This problem involves the *OJ* data set which is part of the ISLR2 package.

(a) Create a training set containing a random sample of 800 observations, and a test set containing the remaining observations.
(b) Fit a tree to the training data, with Purchase as the response and the other variables as predictors. Use the summary () function to produce summary statistics about the tree, and describe the results obtained. What is the training error rate? How many terminal nodes does the tree have?
(c) Type in the name of the tree object in order to get a detailed text output. Pick one of the terminal nodes, and interpret the information displayed.
(d) Create a plot of the tree, and interpret the results.
(e) Predict the response on the test data, and produce a confusion matrix comparing the test labels to the predicted test labels. What is the test error rate?
(f) Apply the cv.tree() function to the training set in order to determine the optimal tree size.
(g) Produce a plot with tree size on the $x$-axis and cross-validated classification error rate on the $y$-axis.
(h) Which tree size corresponds to the lowest cross-validated classification error rate?
(i) Produce a pruned tree corresponding to the optimal tree size obtained using cross-validation. If cross-validation does not lead to selection of a pruned tree, then create a pruned tree with five terminal nodes.
(j) Compare the training error rates between the pruned and unpruned trees. Which is higher?
(k) Compare the test error rates between the pruned and unpruned trees. Which is higher?

Once you have solved the exercise, try to repeat it using another R package, either `rpàrt` or `caret`. Compare the results obtained and comment about the differences observed.

# References
